\textbf{Appendix}\\ Step by Step: Using Integrated Step Selection Analysis to Simulate Wild Dog Dispersal and Assess Landscape Connectivity

### 2022-01-05 Chapter_1/04_Manuscript/Manuscript_Support.tex
Many updates

\documentclass[abstract=off,10pt,a4paper,bibliography=totocnumbered]{article}
\usepackage[paper=a4paper,left=35mm,right=35mm,top=25mm,bottom=30mm]{geometry}
\usepackage[doublespacing]{setspace}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[round]{natbib}
\usepackage{amsmath}
\usepackage{colortbl}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{gensymb}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{enumerate}
\usepackage{enumitem}
\usepackage{subcaption}
\usepackage{booktabs}
\usepackage[hidelinks]{hyperref}
\usepackage[nameinlink]{cleveref}
\usepackage{lineno}
\usepackage{multirow}
\usepackage{arydshln}
% \usepackage[nomarkers, nolists]{endfloat}
\usepackage[flushleft]{threeparttable}
\usepackage{pdflscape}

@@

%------------------------------------------------------------------------------
%	Titlepage: Header
%------------------------------------------------------------------------------
\title{\textbf{Appendix}\\ Step by Step: Using Integrated Step Selection
Analysis to Simulate Wild Dog Dispersal and Assess Landscape Connectivity}

@@

\begin{figure}[hbtp]
 \begin{center}
  \includegraphics[width = \textwidth]{99_MovementModelInterpretation.png}
  \caption{Auxiliary plots that help with the interpretation of the most
   parsimonious movement model from Table S1. The plots were generated
   following recommendations reported in \cite{Fieberg.2021}. Subplots
   \textbf{a1} to \textbf{a8} highlight dispersing wild dogs' movement kernel
   and indicate how the kernel is influenced by interactions with other
   covariates. Subplots \textbf{b1} to \textbf{b5} depict results from
   dispersing wild dogs' habitat kernel and highlight differences in predicted
   relative selection scores (RSS) when varying values of the covariate of
   interest. For each covariate, predictions were made on the range of values
   that was observed in the real data, assuming that all other covariates were
   centered and that steps were realized during periods of ``high'' wild dog
   activity. Plot a1, for example, can be interpreted as follows: the
   probability of realizing a step with a low turning angle is much higher when
   the corresponding step is large. Moreover, b1 can be interpreted as follows:
   relative probability of using a step decreases as the amount of water cover
   along the step increases.}
  \label{Interpretation}
 \end{center}
\end{figure}
% \restoregeometry

@@

%------------------------------------------------------------------------------
%	Appendix S8: Heatmaps
%------------------------------------------------------------------------------
\newpage
\newgeometry{left=35mm,right=35mm,top=25mm,bottom=5mm,footskip=0pt}
\section{Heatmaps in Relation to Number of Simulated Steps}
\begin{figure}[hbtp]
 \begin{center}
  \includegraphics[width = 0.86\textwidth]{99_HeatmapsIndividual.png}
  \caption{Heatmaps produced when considering 125, 500, and 2000 simulated
   steps, respectively. The left panel (a1, a2, a3) was generated based on
   simulations initiated within the main study area, the right panel (b1, b2,
   b3) was generated based on simulations initiated within the buffer area. To
   produce the heatmap presented in the main manuscript (Figure 5), we tallied
   the values from maps a3 and b3.}
  \label{Heatman}
 \end{center}
\end{figure}
\restoregeometry

%------------------------------------------------------------------------------
%	Appendix S9: Evolution of Betweenness Maps
%------------------------------------------------------------------------------
\newpage
\newgeometry{left=35mm,right=35mm,top=25mm,bottom=10mm,footskip=0pt}
\section{Betweenness Maps in Relation to Number of Simulated Steps}
\begin{figure}[hbtp]
 \begin{center}
  \includegraphics[width = 0.86\textwidth]{99_BetweennessIndividual.png}
  \caption{Maps of betweenness scores produced when considering (a) 125, (b)
   500, (c) and 2000 simulated steps, respectively. A high betweenness score
   indicates that the respective area has a high importance for linking other
   regions in the study area.}
  \label{Betweenness}
 \end{center}
\end{figure}
\restoregeometry
%------------------------------------------------------------------------------
%	Appendix S11: Areas Reached
%------------------------------------------------------------------------------
\newpage
\section{Dispersal into other National Parks}
\begin{figure}[hbtp]
 \begin{center}
  \includegraphics[width = \textwidth]{99_AreasReached.png}
  \caption{Relative number of simulated dispersal trajectories that successfully
  moved from one national park into another that is at least as far away as
  indicated on the x-axis. Percentages are given in relation to the number of
  simulated individuals from the national parks in the respective countries. For
  example, over 85\% of all individuals originating from a national park in
  Angola moved from their natal national park into another one. However, the
  percentage gradually decreases as only national parks at higher euclidean
  distances are considered.}
  \label{AreasReached}
 \end{center}
\end{figure}

@@

>>>>

\documentclass[abstract=off,10pt,a4paper,bibliography=totocnumbered]{article}
\usepackage[paper=a4paper,left=35mm,right=35mm,top=25mm,bottom=30mm]{geometry}
\usepackage[doublespacing]{setspace}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[round]{natbib}
\usepackage{amsmath}
\usepackage{colortbl}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{gensymb}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{enumerate}
\usepackage{enumitem}
\usepackage{subcaption}
\usepackage{booktabs}
\usepackage[hidelinks]{hyperref}
\usepackage[nameinlink]{cleveref}
% \usepackage{lineno}
\usepackage{multirow}
\usepackage{arydshln}
% \usepackage[nomarkers, nolists]{endfloat}
\usepackage[flushleft]{threeparttable}
\usepackage{pdflscape}

@@

%------------------------------------------------------------------------------
%	Titlepage: Header
%------------------------------------------------------------------------------
\title{\textbf{Appendix}\\ A Three Steps Workflow for Simulating Dispersal
Trajectories and Assessing Landscape Connectivity: A Case Study on the
Endangered African Wild Dog}

@@

\begin{figure}[hbtp]
 \begin{center}
  \includegraphics[width = \textwidth]{99_MovementModelInterpretation.png}
  \caption{Auxiliary plots that help with the interpretation of the most
  parsimonious movement model from Table S1. The plots were generated following
  recommendations reported in \cite{Fieberg.2021}. Subplots a1 to a8 highlight
  dispersing wild dogs' movement kernel and indicate how the kernel is
  influenced by interactions with other covariates. Subplots b1 to b5 depict
  results from dispersing wild dogs' habitat kernel and highlight differences in
  predicted relative selection scores (RSS) when varying values of the covariate
  of interest. For each covariate, predictions were made on the range of values
  that was observed in the real data, assuming that all other covariates were
  centered and that steps were realized during periods of ``high'' wild dog
  activity. Plot a1, for example, can be interpreted as follows: the probability
  of realizing a step with a low turning angle is much higher when the
  corresponding step is large. Moreover, b1 can be interpreted as follows:
  relative probability of using a step decreases as the amount of water cover
  along the step increases.}
  \label{Interpretation}
 \end{center}
\end{figure}
% \restoregeometry

@@

%------------------------------------------------------------------------------
%	Appendix S8: Heatmaps
%------------------------------------------------------------------------------
\newpage
\newgeometry{left=35mm,right=35mm,top=25mm,bottom=5mm,footskip=0pt}
\section{Heatmaps in Relation to the Number of Simulated Steps}
\begin{figure}[hbtp]
 \begin{center}
  \includegraphics[width = 0.86\textwidth]{99_HeatmapsIndividual.png}
  \caption{Heatmaps produced when considering 125, 500, and 2000 simulated
   steps, respectively. The left panel (a1, a2, a3) was generated based on
   simulations initiated within the main study area, the right panel (b1, b2,
   b3) was generated based on simulations initiated within the buffer area. To
   produce the heatmap presented in the main manuscript (Figure 5), we tallied
   the values from maps a3 and b3.}
  \label{Heatman}
 \end{center}
\end{figure}
\restoregeometry

%------------------------------------------------------------------------------
%	Appendix S9: Evolution of Betweenness Maps
%------------------------------------------------------------------------------
\newpage
\newgeometry{left=35mm,right=35mm,top=25mm,bottom=10mm,footskip=0pt}
\section{Betweenness Maps in Relation to the Number of Simulated Steps}
\begin{figure}[hbtp]
 \begin{center}
  \includegraphics[width = 0.86\textwidth]{99_BetweennessIndividual.png}
  \caption{Maps of betweenness scores produced when considering (a) 125, (b)
   500, (c) and 2000 simulated steps, respectively. A high betweenness score
   indicates that the respective area has a high importance for linking other
   regions in the study area.}
  \label{Betweenness}
 \end{center}
\end{figure}
\restoregeometry

@@

%------------------------------------------------------------------------------
%	Appendix S12: Areas Reached
%------------------------------------------------------------------------------
\newpage
\section{Dispersal into other National Parks}
\begin{figure}[hbtp]
 \begin{center}
  \includegraphics[width = \textwidth]{99_AreasReached.png}
  \caption{Relative number of simulated dispersal trajectories that successfully
  moved from one national park into another that is at least as far away as
  indicated on the x-axis. Percentages are given in relation to the number of
  simulated individuals from the national parks in the respective countries. For
  example, over 85\% of all individuals originating from a national park in
  Angola moved from their natal national park into another one. However, the
  percentage gradually decreases as only national parks at higher euclidean
  distances are considered.}
  \label{AreasReached}
 \end{center}
\end{figure}

### 2022-01-05 Chapter_1/04_Manuscript/Manuscript_Support_2021-12-22.tex
Many updates

%------------------------------------------------------------------------------
%	Titlepage: Header
%------------------------------------------------------------------------------
\title{\textbf{Appendix}\\ A Three Steps Workflow for Simulating Dispersal
Trajectories and Assessing Landscape Connectivity: A Case Study on the
Endangered African Wild Dog}

@@

% Current Date
% \date{\today}

@@

 \textsuperscript{2} Botswana Predator Conservation Program, Private Bag 13,
 Maun, Botswana.

@@

\textbf{Running Title:} Simulating Wild Dog Dispersal Trajectories to Assess
Landscape Connectivity

@@

%------------------------------------------------------------------------------
%	Appendix S8: Heatmaps
%------------------------------------------------------------------------------
\newpage
\newgeometry{left=35mm,right=35mm,top=25mm,bottom=5mm,footskip=0pt}
\section{Heatmaps in Relation to the Number of Simulated Steps}
\begin{figure}[hbtp]
 \begin{center}
  \includegraphics[width = 0.86\textwidth]{99_HeatmapsIndividual.png}
  \caption{Heatmaps produced when considering 125, 500, and 2000 simulated
   steps, respectively. The left panel (a1, a2, a3) was generated based on
   simulations initiated within the main study area, the right panel (b1, b2,
   b3) was generated based on simulations initiated within the buffer area. To
   produce the heatmap presented in the main manuscript (Figure 5), we tallied
   the values from maps a3 and b3.}
  \label{Heatman}
 \end{center}
\end{figure}
\restoregeometry

%------------------------------------------------------------------------------
%	Appendix S9: Evolution of Betweenness Maps
%------------------------------------------------------------------------------
\newpage
\newgeometry{left=35mm,right=35mm,top=25mm,bottom=10mm,footskip=0pt}
\section{Betweenness Maps in Relation to the Number of Simulated Steps}
\begin{figure}[hbtp]
 \begin{center}
  \includegraphics[width = 0.86\textwidth]{99_BetweennessIndividual.png}
  \caption{Maps of betweenness scores produced when considering (a) 125, (b)
   500, (c) and 2000 simulated steps, respectively. A high betweenness score
   indicates that the respective area has a high importance for linking other
   regions in the study area.}
  \label{Betweenness}
 \end{center}
\end{figure}
\restoregeometry

@@

%------------------------------------------------------------------------------
%	Appendix S12: Areas Reached
%------------------------------------------------------------------------------
\newpage
\section{Dispersal into other National Parks}
\begin{figure}[hbtp]
 \begin{center}
  \includegraphics[width = \textwidth]{99_AreasReached.png}
  \caption{Relative number of simulated dispersal trajectories that successfully
  moved from one national park into another that is at least as far away as
  indicated on the x-axis. Percentages are given in relation to the number of
  simulated individuals from the national parks in the respective countries. For
  example, over 85\% of all individuals originating from a national park in
  Angola moved from their natal national park into another one. However, the
  percentage gradually decreases as only national parks at higher euclidean
  distances are considered.}
  \label{AreasReached}
 \end{center}
\end{figure}

>>>>

%------------------------------------------------------------------------------
%	Titlepage: Header
%------------------------------------------------------------------------------
\title{\textbf{Appendix}\\ Step by Step: Using Integrated Step Selection
Analysis to Simulate Wild Dog Dispersal and Assess Landscape Connectivity}

@@

% Current Date
\date{\today}

@@

 \textsuperscript{2} Botswana Predator Conservation, Private Bag 13, Maun,
 Botswana.

@@

 \textbf{Running Title:} Release the Dogs! Simulating Wild Dog Dispersal to
 Assess Landscape Connectivity

@@

%------------------------------------------------------------------------------
%	Appendix S8: Heatmaps
%------------------------------------------------------------------------------
\newpage
\newgeometry{left=35mm,right=35mm,top=25mm,bottom=5mm,footskip=0pt}
\section{Heatmaps in Relation to Number of Simulated Steps}
\begin{figure}[hbtp]
 \begin{center}
  \includegraphics[width = 0.86\textwidth]{99_HeatmapsIndividual.png}
  \caption{Heatmaps produced when considering 125, 500, and 2000 simulated
   steps, respectively. The left panel (a1, a2, a3) was generated based on
   simulations initiated within the main study area, the right panel (b1, b2,
   b3) was generated based on simulations initiated within the buffer area. To
   produce the heatmap presented in the main manuscript (Figure 5), we tallied
   the values from maps a3 and b3.}
  \label{Heatman}
 \end{center}
\end{figure}
\restoregeometry

%------------------------------------------------------------------------------
%	Appendix S9: Evolution of Betweenness Maps
%------------------------------------------------------------------------------
\newpage
\newgeometry{left=35mm,right=35mm,top=25mm,bottom=10mm,footskip=0pt}
\section{Betweenness Maps in Relation to Number of Simulated Steps}
\begin{figure}[hbtp]
 \begin{center}
  \includegraphics[width = 0.86\textwidth]{99_BetweennessIndividual.png}
  \caption{Maps of betweenness scores produced when considering (a) 125, (b)
   500, (c) and 2000 simulated steps, respectively. A high betweenness score
   indicates that the respective area has a high importance for linking other
   regions in the study area.}
  \label{Betweenness}
 \end{center}
\end{figure}
\restoregeometry
%------------------------------------------------------------------------------
%	Appendix S11: Areas Reached
%------------------------------------------------------------------------------
\newpage
\section{Dispersal into other National Parks}
\begin{figure}[hbtp]
 \begin{center}
  \includegraphics[width = \textwidth]{99_AreasReached.png}
  \caption{Relative number of simulated dispersal trajectories that successfully
  moved from one national park into another that is at least as far away as
  indicated on the x-axis. Percentages are given in relation to the number of
  simulated individuals from the national parks in the respective countries. For
  example, over 85\% of all individuals originating from a national park in
  Angola moved from their natal national park into another one. However, the
  percentage gradually decreases as only national parks at higher euclidean
  distances are considered.}
  \label{AreasReached}
 \end{center}
\end{figure}

@@
